\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-14 papers/itsc_2012/final.tex
fig 2 downsized

% Diagram made with gliffy.com. architecture.gxml should enable editing.
\begin{figure*}
  \centering \includegraphics[scale=0.3]{architecture.png}
  \caption{A summary of AORTA's components.}
  \label{fig:arch}
  \vspace{-20pt}
\end{figure*}

@@

\subsection{Agent Reactions}
\label{sec:behaviors}

@@

Dr. Quinlan has certainly been helpful.

What credits do we need to give to OSM?
\commentp{Just citing it is good enough.}

@@

\commentd{Er, these don't look like they're alphabetically sorted. And why is
the Google Maps entry so stretched?}

\bibliographystyle{IEEEtran}
\bibliography{root}

>>>>

% Diagram made with gliffy.com. architecture.gxml should enable editing.
\begin{figure}
  \centering \includegraphics[scale=0.3]{architecture.png}
  \caption{A summary of AORTA's components.}
  \label{fig:arch}
  \vspace{-20pt}
\end{figure}

@@

\subsection{Agent Behavior}
\label{sec:behaviors}

@@

The authors would like to thank Dr. Michael Quinlan for his support during the
seminal stages of AORTA and all OpenStreetMap contributers for providing free
maps.

@@

% They're sorted by order of citation, not alphabetically. IEEEtran.bst confirms
% this is the correct "numerical citation style."
\bibliographystyle{IEEEtran}
\bibliography{root}
